A hybrid approach for news recommender system using optimization methods

### 2021-01-12 paper/paper.tex
updated paper

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}		    % Can be removed after putting your text content
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{doi}            % hyperlink to doi.org
\usepackage{enumitem}       % itemize settings
\usepackage{cleveref}       % reference section with capital letter
\usepackage{xcolor}         % additional colors for hypersetup
\usepackage{booktabs}       % beauful tables
\usepackage{caption}        % table caption margin
\usepackage{placeins}       % floatbarrier

@@

@@

    \newpage

@@

    \subsection{Collaborative filtering recommendation}

@@

    \subsection{Popularity-based recommendation}

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}		    % Can be removed after putting your text content
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{doi}            % hyperlink to doi.org
\usepackage{enumitem}       % itemize settings
\usepackage{cleveref}       % reference section with capital letter
\usepackage{xcolor}         % additional colors for hypersetup
\usepackage{booktabs}       % beauful tables
\usepackage{caption}        % table caption margin
\usepackage{placeins}       % floatbarrier
% Code insertion.
\usepackage[outputdir=build]{minted}

@@

    According to the study \citep{progress}, deep learning techniques are not supposed to beat conceptually and computationally simpler algorithms, so we won't touch them.

    Our goal is to choose optimal algorithm for each of the following tasks:

    \begin{itemize}
        \item \textbf{Collaborative filtering}: generating predictions about the interests of a user by collecting preferences or taste information from other users. It is based on the assumption that if a person A has the same opinion as a person B on an issue, A is more likely to have B's opinion on a different issue than that of a randomly chosen person
        \item \textbf{Content-based filtering}:
        \item \textbf{Session filtering}:
        \item \textbf{Popularity filtering}:
        \item \textbf{Demographic filtering}:
        \item \textbf{Time-based filtering}:
    \end{itemize}

    We face the problem that millions of news are theoretically suitable for being recommended, so it is not correct to use abovementioned methods on such large corpus of data. Instead, as stated in \citep{youtube} paper, we want to implement \mintinline{bash}|candidate generation| $\to$ \mintinline{bash}|ranking| pipeline to reduce number of candidates.

    \subsection{Collaborative filtering}

    There were many studies on this topic, but paper \citep{evaluation} proves that well-tuned basic SVD++ approach beats newely presented algorithms.

@@

@@

    Out goal is to combine state-of-the-art approaches in recommender systems.

    Our approach consists of combining several techniques:

    \begin{itemize}
        \item \textbf{Collaborative filtering}: 
        \item \textbf{Content-based filtering}:
        \item \textbf{Session filtering}:
        \item \textbf{Popularity filtering}:
        \item \textbf{Demographic filtering}:
        \item \textbf{Time-based filtering}:
    \end{itemize}

    Solution consists of 2 parts:

    \begin{itemize}
        \item Candidate generation
        \item Ranking
    \end{itemize}

    \subsection{Architecture overview}

    \subsection{Components overview}

    \subsubsection{Collaborative filtering recommendation}

    We are using SVD++ algorithm.

@@

    \subsubsection{Popularity-based recommendation}
